Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-06-08 talk/icooolps2011/paper.tex
put another explicit sentence saying that the hints go into the interpreter, not the user code.

In this section we will describe two hints that allow the
interpreter author to increase the optimization opportunities for constant
folding. If applied correctly these techniques can give really big speedups by
pre-computing parts of what happens at runtime. On the other
hand, if applied incorrectly they might lead to code bloat, thus making the
resulting program actually slower.

@@

The hint indicates that \texttt{x} is likely a runtime constant and the JIT
should try to perform runtime specialization on it
in the code that follows.\footnote{For technical reasons the promote hint needs
to be written down slightly differently in the actual code.}  When just running
the code, the \texttt{promote} function has no
effect. When tracing, some extra work
is done. Let us assume that this changed function is traced with
the arguments \texttt{4} and \texttt{8}. The trace will be the same, except for one
operation at the beginning.

>>>>

In this section we will describe two hints that allow the
interpreter author to increase the optimization opportunities for constant
folding.
If applied correctly these techniques can give really big speedups by
pre-computing parts of what happens at runtime. On the other
hand, if applied incorrectly they might lead to code bloat, thus making the
resulting program actually slower. Note that these hints are \emph{never} put into the user program, only into the interpreter.

@@

The hint indicates that \texttt{x} is likely a runtime constant and the JIT
should try to perform runtime specialization on it
in the code that follows. When just running
the code, the \texttt{promote} function has no
effect. When tracing, some extra work
is done. Let us assume that this changed function is traced with
the arguments \texttt{4} and \texttt{8}. The trace will be the same, except for one
operation at the beginning.
